\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-10-06 appendices.tex
corrected Isoprimetric Lemma. Went through it with Vardan

\subsection{Proof of Proposition~\ref{prop:ceo_lower_bound}
\label{app:proof:prop_ceo_lower_bound}}

First, we note that when $f(x) = \Ncal(0,\sigma^2)$ and $\pi(\theta) = \Ncal(0,\sigma_\theta^2)$, our distributed setting reduces to the Gaussian CEO problem with $R_1=\ldots = R_n =1$ and $k=1$. Therefore, any MSE attained in our distributed setting is also attained by the CEO and thus the optimal CEO strategy (with arbitrary $k$) provides a lower bound to the MSE in our setting. \\

Consider the minimal MSE $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
from \cite[Eq. 10]{chen2004upper}:
\begin{equation} \label{eq:ceo_optimal_sumrate}
R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
\end{equation}
For the special case of $R_\Sigma = n$ and $L=n$, we get
\begin{equation} \label{eq:ceo_optimal_sumrate2}
n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
\end{equation}
$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders. Therefore, this $D^\star$ provides a lower bound to the CEO MSE with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting. By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that 
\[
D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
\]
We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO MSE while enforcing the condition $R_1=\ldots = R_n = 1$. Indeed, an upper bound for the CEO MSE under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2019}, and leads to
\[
D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
\]
which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.

\subsection{Proof of Theorem~\ref{thm:adpative_lower_bound}
\label{proof:thm:adpative_lower_bound}
}
Consider the following two Lemmas:
\begin{lem} \label{lem:bound_intervals}
Let $f(x)$ be log-concave, symmetric, and differentiable density function such that Assumption~1 holds. For any $x_1 \geq \ldots \geq x_n \in \R$ and $\delta>0$,
\begin{equation}
\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^2 }
{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
\leq  4f^2(0). 
\label{eq:lem_bound_intervals}
\end{equation}
\end{lem}
\begin{lem} \label{lem:fisher_bound}
Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that Assumption~1 holds. For a Borel measurable $A$ set, 
\[
B(X) = \begin{cases} 1,& X \in A, \\
-1, & X \notin A.
\end{cases}
\]
Then the Fisher information of $B$ with respect to $\theta$ is bounded from above by $\eta(0)$.
\end{lem}

@@

The Fisher information of $M$ with respect to $\theta$ is given by
\begin{align}
I_\theta & =  \ex{ \left( \frac{d}{d\theta} \log P\left( M | \theta \right) \right)^2 |\theta } \nonumber \\
& = \frac{ \left(\frac{d}{d\theta} P(M=1|\theta) \right)^2}{P(M=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(M=-1|\theta) \right)^2} {P(M=-1| \theta)} \nonumber \\
& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\ 
& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(M=-1| \theta) } \nonumber \\ 
& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(M=1 | \theta) \left(1-P(M=1|\theta) \right)  }, \nonumber \\
& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
\end{align}
where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$. Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that 
\[
\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
\]
which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$. It is therefore enough to proceed in the proof assuming that $A$ is of the form
\[
A = \cup_{j=1}^k (a_j,b_j),
\]
with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
\begin{align*}
\mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
& = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
\end{align*}
so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
\begin{align}
& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
{ \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
& \times \frac {1} 
{1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
\label{eq:lemma_J}
\end{align}
It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in \R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than 
\[
\max_{t \in \{a_j,b_j, j=1,\ldots,k\} } 4f^2(t) \leq 4 f^2(0), 
\]
where the last transition is due to Assumption~1. 
\QEDA \\

@@

\begin{lem} \label{lem:bound_intervals_delta}
Let $f(x)$ be log-concave, symmetric, and differentiable density function. Let $\delta\geq 0$. Assume that the origin $x=0$ uniquely maximizes the function
\[
\eta_\delta(x) \triangleq  \eta^{1+\delta}(x)/f^\delta(x) = \frac{  \left( f(x) \right)^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}}
\]
and that $\eta_\delta(x)$ is non-increasing in $|x|$. For any $x_1 \ge \ldots \ge x_n \in \R^n$,
\begin{equation}
\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{k=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
\leq  \max_{i} \eta_\delta(x_i).
\label{eq:lem_bound_intervals_delta}
\end{equation}
\end{lem}
In particular, 
\[
\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
\leq \eta_\delta(0)
\]
since $\eta_\delta(x)$ attains its maximum at the origin.

@@

where $s_i \triangleq (-1)^{i+1}$. Set
{\left|\Delta_n(x_1,\ldots,x_n)  \left(1- \Delta_n(x_1,\ldots,x_n) \right) \right|^{1+\delta} }.
We use induction on $n \in \N$ to show that 

@@

Assume that \eqref{eq:lemm:interval_bounds:to_show} holds for all integers up to $n = N$ and for any $x_1 \ge \ldots \ge x_n$. Consider the case $n = N+1$. Let $i^*$ be the index such that $x_{i^*}$ has minimal absolute value among $x_1,\ldots,x_N$. The assumption on $\eta_\delta(x)$ implies that

@@

& g(y_1,\ldots,y_N) \triangleq  \frac{\left| \delta_N(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N) )\right|^{2+\delta}}{
\left|\Delta_N(y_1,\ldots,y_k,x_{i^*},y_{k+1}\ldots,y_N)  \right) \left(1 -\Delta_N(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N))  \right|^{1+\delta}
} .
The claim in the lemma is obtained by taking $y_i=x_{i'}$ where $i'$ is the $i$th element in $\{1,\ldots,N+1\}\setminus \{i^*\}$. It is therefore enough to prove that 

@@

The maximal value of $g(y_1,\ldots,y_N)$ is attained for the same $(y_1,\ldots,y_N) \in A_{N+1}(x^*,k)$ that maximizes

@@

The partial derivative of $\log(g)(y_1,\ldots,y_N)$ with respect to $y_i$ within the interior of $A_N(x^*,k)$ is given by

@@

if $N$ is even, or

@@

& g(y_1,\ldots,y_N) = \frac{\left| s_1f(y_1)+s_{N+1}f(x_{i^*})  \right|^{2+\delta}} { 
\left|  s_1F(y_N) + s_{N+1}F(x_{i^*}) \right|^{1+ \delta} 
\left| 1 - (s_1F(y_1) + s_{N+1}F(x_{i^*})) \right|^{1+ \delta} } 

@@

if $N$ is odd and $y_1 < x^*$. Form the induction assumption, the last display is bounded from above by $\eta_\delta(x_{i^*})$. The case where $N$ is odd and $y_1 > x^*$ is similar. 

@@

We now consider the possibility that the maximum of $g(y_1,\ldots,y_N)$ is attained at the boundaries of $A_N(x^*,k)$. For boundary points for which $y_i = y_{i+1}$ for some $i$, the contribution of $y_i$ and $y_{i+1}$ to $g(y_1,\ldots,y_N)$ is zero and the induction assumption for $n=N-1$ implies that 

@@

at these points. The remaining boundary points of $A_N(x^*,k)$ are covered by the following cases:

@@

Under case (4), set 

@@

Note that whenever $d>0$, 

@@

In the case where $c'(x)$ is not necessarily strictly decreasing, we approximate $c(x)$ using another concave symmetric function whose derivative is always negative except at the origin. For $\alpha>0$ consider the function  $f_\alpha(x) = \kappa(\alpha) e^{\sgn(c(x))|c(x)|^{1+\alpha}}$, where $\kappa(\alpha)$ is chosen such that $f_\alpha(x)$ is a probability density function. Then $c_\alpha(x)$ is concave, symmetric, and differentiable with

@@

Now $c_\alpha'(x)$ is non-increasing since it is the derivative of a concave function. It can be verified that it is non-constant on any interval (because $c(x)$ is non-constant and $c'(x)$ is non-increasing), and hence an injection. It follows from the first part of the proof that, for any $\alpha>0$,

@@

\subsection{Proof of Theorem~\ref{thm:sgd}
\label{proof:thm:sgd}
}
The algorithm given in \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}.

@@

In order to prove this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$. The first expression on the RHS on \eqref{eq:Polyak_expansion} goes to zero in variance. In addition, 
\begin{align*}
& \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 }  = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
& = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0. 
\end{align*}
We obtain
\begin{equation}
\sqrt{n} \bar{\Delta}^1_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1), \label{eq:Polyak_expansion_aux_process}
\end{equation}

@@

Lemma~\ref{lem:PJ_converging_sum} shows that 
\begin{align}
\sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda}}{\sqrt{i}}  < \infty \label{eq:PJ_converging_sum},
\end{align}
hence the Kronecker lemma implies
\[
\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \to 0.
\]
For the term \eqref{eq:PJ_proof2}, set 
\[
\epsilon_i \triangleq \psi(\Delta_{i-1}) + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i).
\]
For $a>0$ and $n \in \N$, define the event
\[
A_{n,a} \triangleq \left\{ \sum_{i=1}^{n-1} \frac{|\epsilon_i|}{\sqrt{i}}  \geq a  \right\}. 
\]
By Markov's inequality, we have
\begin{align}
\ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } \leq \frac{1}{a} \sum_{i=1}^{n-1} \frac{ \ex{|\epsilon_i| \Delta_{i-1} \mid }}{\sqrt{i}}. \label{eq:PJ_proof_3}
\end{align}
Using \eqref{eq:Polyak_Juditsky_cond3} and \eqref{eq:PJ_additional_cond}, there exists $K'$ and $\lambda'>0$ such that
\begin{align*}
& \ex{ |\epsilon_i| | \Delta_{i-1}}  \leq |\psi(\Delta_{i-1})| + \left| \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i) \right|  \\
& \leq K' |\Delta_{i-1}|^{1+\lambda}. 
\end{align*}
Plugging this bound in \eqref{eq:PJ_proof_3} and using Lemma~\ref{lem:PJ_converging_sum},we obtain 
\[
\Prob(A_{n,a}) = \ex{ \ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } } \leq  \frac{K''}{a}
\]
for some constant $K''$. It follows that for any $\epsilon$, we may choose $a$ large enough such that 
\[
\sup_{n} \Prob(A_{n,a}) < \epsilon.
\]
This implies that for any $\epsilon>0$,
\[
\Prob \left( \sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty \right) \geq 1-\epsilon,
\]
and hence 
\[
\sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty
\]
almost surely. The Kronecker lemma now implies 
\[
\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left|\epsilon_i\right| \to 0,
\]
hence the term \eqref{eq:PJ_proof2} satisfies
\[
\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right) \epsilon_i \leq \frac{K'''}{\sqrt{n}} \sum_{i=1}^{n-1} |\epsilon_i| \to 0. 
\]
This conclude the proof of part (i).

>>>>

\subsection{Proof of Proposition~\ref{prop:CEO}
\label{app:proof:CEO}}

%
Denote by $D^\star$ the optimal MSE in the Gaussian CEO with $L$ observers and under a total sum-rate $r = r_1 + \ldots +r_L$. An expression for $D^\star$ as a function of $r$ is give as \cite[Eq. 10]{chen2004upper}:
\begin{equation} \label{eq:ceo_optimal_sumrate}
r = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
\end{equation}
For the special case where $r = n$ and $L=n$, we have
\begin{equation} \label{eq:ceo_optimal_sumrate2}
n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
\end{equation}
Consider the distributed encoding setting (iii) in the case where $f(x) = \Ncal(0,\sigma^2)$ and the prior on $\Theta$ is $\pi = \Ncal(0,\sigma_\theta^2)$. The Gaussian CEO problem of \cite{viswanathan1997quadratic} with a unit bitrate $r_1=\ldots = r_n =1$ at each terminal and blocklength $k=1$ reduces to our distributed setting (iii). Since $D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describes the MSE in the CEO setting under an optimal allocation of the sum-rate $r = n$ among $n$ encoders, it provides a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting. By considering the limit $n\rightarrow \infty$ in \eqref{eq:ceo_optimal_sumrate2}, we see that 
\[
D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
\]
This implies Proposition~\ref{prop:CEO}. 
%We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the MSE in the CEO setting while enforcing the condition $r_1=\ldots = r_n = 1$. Indeed, an upper bound for the CEO MSE under the condition $r_1=\ldots = r_n = 1$ follows from \cite{KipnisRini2019}, and leads to
%\[
%D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
%\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
%\]
%which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.

\subsection{Proof of Theorem~\ref{thm:adpative_lower_bound}
\label{proof:thm:adpative_lower_bound}
}
Consider the following two Lemmas:
\begin{lem} \label{lem:bound_intervals}
Let $f(x)$ be log-concave, symmetric, and differentiable density function such that Assumption~1 holds. For any $x_1 \geq \ldots \geq x_n \in \R$,
\begin{equation}
\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^2 }
{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
\leq  4f^2(0). 
\label{eq:lem_bound_intervals}
\end{equation}
\end{lem}
\begin{lem} \label{lem:fisher_bound}
Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that Assumption~1 holds. For a Borel measurable $A$ set, 
\[
B(X) = \begin{cases} 1,& X \in A, \\
-1, & X \notin A.
\end{cases}
\]
Then the Fisher information of $B$ with respect to $\theta$ is bounded from above by $\eta(0)$.
\end{lem}

@@

The Fisher information of $B$ with respect to $\theta$ is given by
\begin{align}
I_\theta & =  \ex{ \left( \frac{d}{d\theta} \log P\left( B | \theta \right) \right)^2 |\theta } \nonumber \\
& = \frac{ \left(\frac{d}{d\theta} P(B=1|\theta) \right)^2}{P(B=1| \theta)} + \frac{ \left(\frac{d}{d\theta} P(B=-1|\theta) \right)^2} {P(B=-1| \theta)} \nonumber \\
& =  \frac{ \left( \frac{d}{d\theta} \int_A f \left( x-\theta\right)dx \right)^2} { P(B=1| \theta) } + \frac{ \left( \frac{d}{d\theta}\int_A f \left( x-\theta \right)dx \right)^2} { P(B=-1| \theta) } \nonumber \\ 
& \overset{(a)}{=} \frac{ \left( - \int_A f' \left( x-\theta \right)dx \right)^2} { P(B=1| \theta) } + \frac{ \left(- \int_A f' \left( x-\theta \right)dx \right)^2} { P(B=-1| \theta) } \nonumber \\ 
& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right)^2 }{  P(B=1 | \theta) \left(1-P(B=1|\theta) \right)  }, \nonumber \\
& = \frac{\left( \int_A f'\left( x-\theta \right) dx \right) \left( \int_A f'\left( x-\theta \right) dx \right)}{ \left( \int_A f \left( x-\theta \right) dx \right)  \left(1- \int_A f \left( x-\theta \right) dx \right) }, \label{eq:lem_fisher_bound_proof1}
\end{align}
where differentiation under the integral sign in $(a)$ is possible since $f(x)$ is differentiable with continuous derivative $f'(x)$. Regularity of the Lebesgue measure implies that for any $\epsilon>0$, there exists a finite number $k$ of disjoint open intervals $I_1,\ldots I_k$ such that 
\[
\int_{A\setminus \cup_{j=1}^k I_j }  dx < \epsilon,
\]
which implies that for any $\epsilon' > 0$, the set $A$ in \eqref{eq:lem_fisher_bound_proof1} can be replaced by a finite union of disjoint intervals without increasing $I_\theta$ by more than $\epsilon'$. It is therefore enough to proceed in the proof assuming that $A$ is of the form
\[
A = \cup_{j=1}^k (a_j,b_j),
\]
with $\infty \leq a_1 \leq \ldots a_k$, $b_1 \leq b_k \leq \infty$ and $a_j \leq b_j$ for $j=1,\ldots,k$. Under this assumption we have
\begin{align*}
\mathbb P(B_n=1| \theta) & = \sum_{j=1}^k \mathbb P\left(X_n \in (a_j,b_j) \right)  \\
& = \sum_{j=1}^k \left( F \left(b_j-\theta\right) -  F \left(a_j-\theta\right)  \right),
\end{align*}
so \eqref{eq:lem_fisher_bound_proof1} can be rewritten as
\begin{align}
& =   \frac { \left( \sum_{j=1}^{k} f \left(a_j-\theta \right) - f \left( b_j-\theta \right)  \right)^2 } 
{ \left( \sum_{j=1}^k F \left( b_j-\theta \right) - F \left( a_j-\theta \right)  \right) }  \nonumber \\
& \times \frac {1} 
{1- \left( \sum_{j=1}^k F \left(  b_j-\theta \right) - F \left( a_j-\theta \right)  \right) } 
\label{eq:lemma_J}
\end{align}
It follows from Lemma~\ref{lem:bound_intervals} that for any $\theta \in \R$ and any choice of the intervals endpoints, \eqref{eq:lemma_J} is smaller than 
\[
\max_{t \in \{a_j,b_j, j=1,\ldots,k\} } 4f^2(t) \leq 4 f^2(0), 
\]
where the last transition is due to Assumption~1. 
\QEDA \\

@@

\begin{lem} \label{lem:bound_intervals_delta}
Let $f(x)$ be log-concave, symmetric, and differentiable density function. Let $\delta\geq 0$. Assume that the origin $x=0$ uniquely maximizes the function
\[
\eta_\delta(x) \triangleq  \eta^{1+\delta}(x)/f^\delta(x) = \frac{  \left( f(x) \right)^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}}
\]
and that $\eta_\delta(x)$ is non-increasing in $|x|$. For any $x_1 \ge \ldots \ge x_n \in \R^n$,
\begin{equation}
\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{k=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
\leq  \max_{i} \eta_\delta(x_i).
\label{eq:lem_bound_intervals_delta}
\end{equation}
\end{lem}
In particular, 
\[
\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
\leq \eta_\delta(0) = 4^{1+\delta} f^{2+\delta}(0).
\]

@@

where $s_i \triangleq (-1)^{i+1}$. We use induction on $n \in \N$ to show that 

@@

Assume that \eqref{eq:lemm:interval_bounds:to_show} holds for all integers up to $n = N$ and for any $x_1 \ge \ldots \ge x_N$. Consider the case $n = N+1$. Let $i^*$ be the index such that $x_{i^*}$ has minimal absolute value among $x_1,\ldots,x_N$. The assumption on $\eta_\delta(x)$ implies that

@@

& g(y_1,\ldots,y_N) \triangleq g(y_1,\ldots,y_N|x^*,k) \\
&  \triangleq  \frac{\left| \delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N) )\right|^{2+\delta}}{
\left|\Delta_{N+1}(y_1,\ldots,y_k,x_{i^*},y_{k+1}\ldots,y_N)  (1 -\Delta_{N+1}(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N)  \right|^{1+\delta}
} \label{eq:g_def}.
The LHS of \eqref{eq:lemm:interval_bounds:to_show} is obtained by taking $y_i=x_{k_i}$ where $k_i$ is the $i$th element in $\{1,\ldots,N+1\}\setminus \{i^*\}$. It is therefore enough to prove that 

@@

The maximal value of $g(y_1,\ldots,y_N)$ is attained for the same $(y_1,\ldots,y_N) \in A_N(x^*,k)$ that maximizes

@@

Within the interior of $A_N(x^*,k)$, all three expressions in \eqref{eq:g_def} within an absolute value are positive. It follows that partial derivative of $\log(g)(y_1,\ldots,y_N)$ with respect to $y_i$ within the interior of $A_N(x^*,k)$ is given by

@@

if $N$ is even. If $N$ is odd and $y_1 = \ldots = y_N > x^*$, then 

@@

& g(y_1,\ldots,y_N) = \frac{\left| f(y_1)-f(x_{i^*})  \right|^{2+\delta}} { 
\left|  F(y_1) - F(x_{i^*}) \right|^{1+ \delta} 
\left| 1 - (F(y_1) -F(x_{i^*})) \right|^{1+ \delta} } 

@@

which is bounded from from above by $\eta_\delta(x_{i^*})$ by the induction hypothesis. The case where $N$ is odd and $-x^* \leq y_1 = \ldots = y_N$ is similar. 

@@

We now consider the possibility that the maximum of $g(y_1,\ldots,y_N)$ is attained at the boundaries of $A_N(x^*,k)$. At boundary points for which $y_i = y_{i+1}$ for some $i$, the contribution of $y_i$ and $y_{i+1}$ to $g(y_1,\ldots,y_N)$ is zero and the induction assumption for $n=N-1$ implies that 

@@

The remaining boundary points of $A_N(x^*,k)$ are covered by the following cases:

@@

Finally, under case (4), set 

@@

Whenever $d>0$, 

@@

In the case where $c'(x)$ is not necessarily strictly decreasing, we approximate $c(x)$ using another concave symmetric function whose derivative is always negative except, perhaps, at the origin. For $\alpha>0$ consider the function  $f_\alpha(x) = \kappa(\alpha) e^{\sgn(c(x))|c(x)|^{1+\alpha}}$, where $\kappa(\alpha)$ is chosen such that $f_\alpha(x)$ is a probability density function. Then $c_\alpha(x)$ is concave, symmetric, and differentiable with

@@

Now $c_\alpha'(x)$ is non-increasing since it is the derivative of a concave function. Furthermore, since $c(x)$ is non-constant on any interval and $c'(x)$ is non-increasing, $c_\alpha'(x)$ is non-constant on any interval hence an injection. It follows from the first part of the proof that, for any $\alpha>0$,

@@

\subsection{Proof of Theorem~\ref{thm:sgd}
\label{proof:thm:sgd}
}
The estimation algorithm of \eqref{eq:sgd_alg} and \eqref{eq:sgd_est} is a special case of a more general class of estimation procedures given in \cite{polyak1992acceleration} and \cite{polyak1990new}. The proof of Theorem~\ref{thm:sgd} relies on various results from these works.

@@

In order to prove this claim, use Lemma~\ref{lem:Polyak_expansion} with $A = \psi'(0)$ and $\xi_i = -\varphi(Z_i)$. The first expression on the RHS of \eqref{eq:Polyak_expansion} goes to zero in variance. In addition, 
\begin{align*}
& \ex{ \left( \frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} w_i^n \xi_i \right)^2 }  = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \xi_i^2} + \frac{1}{n}  \sum_{i\neq j}^n w_i^n w_j^n \ex{ \xi_i \xi_j} \\
& = \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \ex{ \varphi(Z_i)^2} = \chi(0) \frac{1}{n}  \sum_{i=1}^n (w_i^n)^2 \to 0. 
\end{align*}
We obtain
\begin{equation}
\sqrt{n} \bar{\Delta}^1_n = -\frac{1}{\sqrt{n}} \frac{1}{\psi'(0)} \sum_{i=1}^{n-1} \varphi(Z_i)+ o_{p.n}(1), \label{eq:Polyak_expansion_aux_process}
\end{equation}

@@

Lemma~\ref{lem:PJ_converging_sum} shows that 
\begin{align}
\sum_{i=1}^\infty \frac{|\Delta_i|^{1+\lambda}}{\sqrt{i}}  < \infty \label{eq:PJ_converging_sum},
\end{align}
hence the Kronecker lemma implies
\[
\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right)  \left( \psi'(0) \Delta_{i-1}  - \psi(\Delta_{i-1}) \right) \to 0.
\]
For the term \eqref{eq:PJ_proof2}, set 
\[
\epsilon_i \triangleq \psi(\Delta_{i-1}) + \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i).
\]
For $a>0$ and $n \in \N$, define the event
\[
A_{n,a} \triangleq \left\{ \sum_{i=1}^{n-1} \frac{|\epsilon_i|}{\sqrt{i}}  \geq a  \right\}. 
\]
By Markov's inequality, we have
\begin{align}
\ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } \leq \frac{1}{a} \sum_{i=1}^{n-1} \frac{ \ex{|\epsilon_i| \Delta_{i-1} \mid }}{\sqrt{i}}. \label{eq:PJ_proof_3}
\end{align}
Using \eqref{eq:Polyak_Juditsky_cond3} and \eqref{eq:PJ_additional_cond}, there exists $K'$ and $\lambda'>0$ such that
\begin{align*}
& \ex{ |\epsilon_i| | \Delta_{i-1}}  \leq |\psi(\Delta_{i-1})| + \left| \varphi(Z_i) - \varphi(\Delta_{i-1}+Z_i) \right|  \\
& \leq K' |\Delta_{i-1}|^{1+\lambda}. 
\end{align*}
Plugging this bound in \eqref{eq:PJ_proof_3} and using Lemma~\ref{lem:PJ_converging_sum}, we obtain 
\[
\Prob(A_{n,a}) = \ex{ \ex{\mathbf 1_{A_{n,a}}   \mid \Delta_0,\ldots,\Delta_{n-1} } } \leq  \frac{K''}{a}
\]
for some constant $K''$. It follows that for any $\epsilon$, we may choose $a$ large enough such that 
\[
\sup_{n} \Prob(A_{n,a}) < \epsilon.
\]
This implies that for any $\epsilon>0$,
\[
\Prob \left( \sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty \right) \geq 1-\epsilon,
\]
and hence 
\[
\sum_{i=1}^\infty \frac{|\epsilon_i|}{\sqrt{i}} < \infty
\]
almost surely. The Kronecker lemma now implies 
\[
\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left|\epsilon_i\right| \to 0,
\]
hence the term \eqref{eq:PJ_proof2} satisfies
\[
\frac{1}{\sqrt{n}} \sum_{i=1}^{n-1} \left( \frac{1}{\psi'(0)}  + w_i^n \right) \epsilon_i \leq \frac{K'''}{\sqrt{n}} \sum_{i=1}^{n-1} |\epsilon_i| \to 0. 
\]
This conclude the proof of part (i).
